Efficient ancestry and mutation simulation with msprime 1.0

### 2021-11-25 paper.tex
Caution about neutral sims.
Closes #228

% and finally lay out future plans for
% further open-source development of what we hope will become an industry
% standard piece of computational infrastructure for the genetics community.

@@

Demography
&
Improved interface with integrated metadata and referencing populations by
name. Import from Newick species tree, *BEAST~\citep{heled2009bayesian},
and Demes~\citep{gower2022demes}. Numerical methods to compute
coalescence rates.\\

@@

What does this tell us about run time for simulating time-varying population sizes?
Suppose that population size today is $N_1$,
while $T$ generations ago it was $N_2$.
Does the run time depend more on $4 N_1 L$ or $4 N_2 L$?
The answer depends on how $T$ compares to $N_1$: if $T/N_1$ is large,
then run time will be similar to a population of size $N_1$;
while if $T/N_1$ is small, it will be similar to a population of size $N_2$.
For instance, in many agricultural species $N_1 \propto 100$, while $N_2 \propto 10^5$,
and the run time will depend critically on $T$---in other words,
simulation will be quick in a species with a strong domestication bottleneck,
and slow otherwise.

>>>>

The efficiency of coalescent simulations depends
crucially on the assumption of neutrality, and it is important
to note that there are many situations in which this will be a poor approximation
of biological reality~\citep{johri2021statistical}.
In particular the existence of pervasive background
selection in many
species~\citep{charlesworth1993effect,charlesworth1995pattern,charlesworth2021effects}
means that care must be taken to ensure that the results of
neutral simulations are appropriate for the study in question.

@@

Demography
&
Improved interface with integrated metadata and referencing populations by
name. Import from Newick species tree, *BEAST~\citep{heled2009bayesian},
and Demes~\citep{gower2021demes}. Numerical methods to compute
coalescence rates.\\

@@

What does this tell us about run time for simulating time-varying population sizes?
Suppose that population size today is $N_1$,
while $T$ generations ago it was $N_2$.
Does the run time depend more on $4 N_1 L$ or $4 N_2 L$?
The answer depends on how $T$ compares to $N_1$:
if $T / N_1 \ll 1$ then the number of extant lineages remaining after $T$
generations is likely to be substantial, and the algorithm runtime is primarily
determined by $N_2$. Conversely, if $T / N_1 \gg 1$, then few extant
lineages are likely to remain by time $T$ and runtime depends mainly on $N_1$.
For instance, in many agricultural species $N_1 \approx 100$, while $N_2
\approx 10^5$,
and the run time will depend critically on $T$---in other words,
simulation will be quick in a species with a strong domestication bottleneck,
and slow otherwise.
